---
title: "Task12"
author: "Mallory Dickerson"
date: "10/4/2022"
output: 
  html_document:
    keep_md: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(readr)
library(haven)
library(readxl)
library(downloader)
```

```{r}
dat1 <- tempfile()
download.file("https://github.com/WJC-Data-Science/DTS350/raw/master/Dart_Expert_Dow_6month_anova/Dart_Expert_Dow_6month_anova.csv", "dat1")
Dart1 <- read_csv("dat1")

dat2 <- tempfile()
download.file("https://github.com/WJC-Data-Science/DTS350/raw/master/Dart_Expert_Dow_6month_anova/Dart_Expert_Dow_6month_anova.RDS", "dat2", mode = "wb")
read_rds("dat2")
Dart2 <- read_rds("dat2")

dat3 <- tempfile()
download.file("https://github.com/WJC-Data-Science/DTS350/raw/master/Dart_Expert_Dow_6month_anova/Dart_Expert_Dow_6month_anova.dta", dat3, mode = "wb")
read_dta(dat3)
Dart3 <- read_dta(dat3)

dat4 <- tempfile()
download.file("https://github.com/WJC-Data-Science/DTS350/raw/master/Dart_Expert_Dow_6month_anova/Dart_Expert_Dow_6month_anova.sav", "dat4", mode = "wb")
read_sav("dat4")
Dart4 <- read_sav("dat4")

dat5 <- tempfile()
download.file("https://github.com/WJC-Data-Science/DTS350/raw/master/Dart_Expert_Dow_6month_anova/Dart_Expert_Dow_6month_anova.xlsx", "dat5", mode = "wb")
read_xlsx("dat5")
Dart5 <- read_xlsx("dat5")

```

```{r}
all_equal(Dart1, Dart2, Dart3, convert = TRUE)
all_equal(Dart1, Dart4, Dart5, convert = TRUE)
```
```{r BoxPlot}
head(Dart1)
ggplot() +
  geom_boxplot(data = Dart1, aes(x = variable, y = value, fill = variable)) +
  labs(x = "Variable",
       y = "Value",
       title = "Variable vs Value Using Boxplot") +
  theme_bw()
```
The boxplot shows that PROS has the highest return, but that it has the largest range, leaving open
the possibilty that you don't gain as much as is shown on the high end. The Dow Jones operates in a much narrower
range, with not as much potential on the upside, but also not as much risk on the downside.
```{r JitterReturn}
ggplot() +
  geom_jitter(data = Dart1, aes(x = variable, y = value, color = variable)) +
  labs(x = "Variable",
       y ="Value",
       title = "Varible vs Value Using Jitter") +
  theme_bw()
```
The jitter plot shows essentially the same thing as the boxplot. The Dow Jones return is much more compressed 
compared to DARTS and PROS. The jitter plot also allows us to see that PROS and DARTS have similar spread in 
their range.



```{r AVG_return}
ggplot() +
  geom_line(data = Dart1, aes(x = contest_period, y = value, group = variable, color = variable)) +
  labs(x = "Contest Period",
       y = "Value",
       title = "Contest Period VS Value") +
  theme_bw()
```
The line plot shows us that there is more volatility in DARTS and PROS than in Dow Jones. 
Volatility makes it difficult to realize gains that are lasting, though it also creates opportunity in the 
short term.


```{r tidying the data}
head(Dart1)

Dart1Tidy <- Dart1 %>%
   mutate(contest_period = str_replace_all(contest_period, '19', '_19'),
         contest_period = str_replace(contest_period, 'Febuary', 'February'),
         contest_period = str_replace(contest_period, 'Dec._1993', 'December_1993')) %>%
  separate(contest_period, into = c("month", "year_end"), sep = "-") %>%
  separate(year_end, into = c("month", "year"), sep = "_") %>%
  arrange(factor(month, levels = month.name))

head(Dart1Tidy)
view(Dart1Tidy)

#saving as RDS
saveRDS(Dart1Tidy, file = "Dart1Tidy.rds")

```


```{r Plot}
ggplot(data = Dart1Tidy, aes(x = year, y = value, group = month)) +
  geom_point(aes(color = variable)) +
  geom_line(aes(color = variable)) +
  facet_wrap(~month, scales = "free") +
  labs(x = "Year",
       y = "Returns",
       title = "Returns By Month from 1990 through 1998") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45))
```
It looks like volatility is significant for PROS and DARTS, making it difficult to have a long term investment
strategy. 



```{r}
FinalTable <- Dart1 %>%
  filter(variable == "DJIA") %>%
  mutate(contest_period = str_replace_all(contest_period, "19", "_19"),
         contest_period = str_replace(contest_period, "Febuary", "February"),
         contest_period = str_replace(contest_period, "Dec._1993", "December_1993")) %>%
  separate(contest_period, into = c("Month", "Year_end"), sep = "-") %>%
  separate(Year_end, into = c("Month", "Year"), sep = "_") %>%
  pivot_wider(names_from = "Year", values_from = "value") %>%
  arrange(factor(Month, levels = month.name)) %>%
  select(-variable)
FinalTable
```

