---
title: "CaseStudy7"
author: "Mallory Dickerson"
date: "10/6/2022"
output: 
  html_document:
    keep_md: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(haven)
library(readr)
library(readxl)
library(downloader)
library(foreign)
```

```{r}
dat1 <- tempfile()
download.file("https://github.com/WJC-Data-Science/DTS350/raw/master/CaseStudy7Data/heights.csv", "dat1")
readLines("dat1", n = 5) 
read_csv("dat1", skip = 2)
Height_csv <- read_csv("dat1", skip = 2, col_names = c("earn", "height", "sex", "ed", "age", "race"))

dat2 <- tempfile()
download.file("https://github.com/WJC-Data-Science/DTS350/raw/master/Height.xlsx", "dat2", mode = "wb")
read_xlsx("dat2", skip = 2)
Height_xlsx <- read_xlsx("dat2", skip = 2)

dat3 <- tempfile()
download.file("https://github.com/WJC-Data-Science/DTS350/raw/master/CaseStudy7Data/B6090.DBF", "dat3", mode = "wb")
read.dbf("dat3")
Height_dbf <- read.dbf("dat3")


dat4 <- tempfile()
download.file("https://github.com/WJC-Data-Science/DTS350/raw/master/germanconscr.dta", "dat4", mode = "wb")
read_stata("dat4")
German_conscript_stata <- read_stata("dat4")

dat5 <- tempfile()
download.file("https://github.com/WJC-Data-Science/DTS350/raw/master/germanprison.dta", "dat5", mode = "wb")
read_stata("dat5")
Bavarian_heights <- read_stata("dat5")

dat6 <- tempfile()
download.file("http://www.ssc.wisc.edu/nsfh/wave3/NSFH3%20Apr%202005%20release/main05022005.sav", "dat6", mode = "wb")
read_sav("dat6")
Wisco <- read_sav("dat6")
```

tidying CSV file
```{r}
bls <- Height_csv %>%  
  mutate(birth_year = 1950,
         height.in = height,
         height.cm = height.in * 2.54,
         study_id = 'BLS Wage and Height Data in 1950') %>%  
  select(birth_year, height.cm, height.in, study_id)

```

tidying xlsx file 
```{r}
WorldData <- Height_xlsx %>%  
  pivot_longer(3:203, names_to = "years", values_to = "heights.cm", values_drop_na = TRUE) %>%   
  mutate(year_decade = years, 
         height.in = heights.cm / 2.54) %>%  
  separate(years, into = c("century", "decade"), sep = -2) %>%  
  separate(decade, into = c("decade", "year"), sep = -1)
head(WorldData)
write.csv(WorldData,"worlddata.csv", row.names = TRUE)
head(WorldData)
```


tidying DBF file
```{r}
height_dbf_tidy <- Height_dbf %>%  
  mutate(height.in = CMETER / 2.54,
         height.cm = CMETER,
         birth_year = SJ,
         study_id = 'Heights of SE and SW german soldiers, 18th century') %>%  
  select(height.in, height.cm, birth_year, study_id)
```



tidying german male height dta file
```{r}
german_conscript_tidy <- German_conscript_stata %>%  mutate(birth_year = bdec, 
         height.cm = height, 
         height.in = height.cm / 2.54,
         study_id = 'German male conscripts in Bavaria, 19th centery') %>%  
  select(birth_year, height.cm, height.in, study_id)
german_conscript_tidy
```

tidying bavarian male height dta
```{r}
bavarian_heights_tidy <- Bavarian_heights %>%
  mutate(birth_year = bdec,
         height.cm = height,
         height.in = height.cm / 2.54,
         study_id = 'Heights of bavarian male conscripts, 19th century') %>%
  select(birth_year, height.in, height.cm, study_id)

bavarian_heights_tidy
```


tidying wisco file
```{r}
wisco_tidy <- Wisco %>%  
  mutate(birth_year = DOBY + 1900, height.in = RT216F*12 + RT216I, height.cm = height.in * 2.54, study_id = 'National Survey (Wisconsin), 19th century') %>%  
  select(birth_year, height.in, height.cm, study_id)
wisco_tidy
```


combining all data sets
```{r}
combined <- bind_rows(bls, height_dbf_tidy, german_conscript_tidy, bavarian_heights_tidy, wisco_tidy)

head(combined)
write.csv(combined,"height_data.csv", row.names = TRUE)
```

Germany plot
```{r}
germany <- WorldData %>%
  filter(`Continent, Region, Country` == "Germany")

ggplot() + 
  geom_boxplot(data = WorldData, aes(x = decade, y = height.in)) +
  geom_point(data = germany, aes(x = decade, y = height.in, color = "red")) +
  labs(
    x = "Decade",
    y = "Height in Inches",
    title = "Heights across the World compared to Germany",
    subtitle = "Germany highlighted in red"
  ) +
  theme_bw()
```
The boxplot demonstrates that across decades, height ranges and average height has not fluctuated much.
Averages are all above 65 inches and below 67 inches. I'm not sure you can tell if height is increasing across
decades. However, the graph does demonstrate that German male height is increasing across decades.

```{r}
head(combined)
ggplot(data = combined, aes(x = birth_year, y = height.in)) +
  geom_col() +
  facet_wrap(~study_id, scales = "free") +
  labs(x = "Year",
       y = "Height in Inches",
       title = "Height Distribution Across Years",
       subtitle = "Faceted by different studies") +
  theme_bw()
```
It is difficult to decide whether height is increasing across the different studies. 
