---
title: "task14"
author: "Mallory Dickerson"
date: "10/17/2022"
output: 
  html_document:
    keep_md: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(downloader)
```

```{r loading data}
bible <- tempfile()
download.file("https://github.com/WJC-Data-Science/DTS350/raw/master/bible.csv", "bible", mode = "wb")
bible_data <- read_csv("bible")
head(bible_data)
str(bible_data)
```


filtering for new testament 
```{r NT}
NT <- bible_data %>%
  filter(volume_title == "New Testament") %>%
  select(scripture_text)
head(NT)
```

filtering for old testament
```{r OT}
OT <- bible_data %>%
  filter(volume_title == "Old Testament") %>%
  select(scripture_text)
head(OT)
```


```{r getting verse length}
verse_length <- function(df) {
  v_length <- vector("integer", 0)
  for (row in df) {
    v_length <- append(v_length, str_length(row))
  }
  
  v_length
}
```

verse length averages
```{r averages}
mean(verse_length(NT))

mean(verse_length(OT))
```


getting LORD word occurance
```{r LORD}
str_length(str_extract_all(NT, "(?i)lord"))

str_length(str_extract_all(OT, "(?i)lord"))
```


data viz
```{r distribution}
verse_data <- as.data.frame(verse_length(NT))
head(verse_data)
ggplot(data = verse_data) +
  geom_histogram(aes(x = verse_length(NT), color = 'grey')) +
  labs(
    x = "Verse Length",
    y = "Occurance of Verse Length",
    title = 'New Testament Verse Length Occurances'
  ) +
  theme_bw()

```

Answering the questions for the task, we see that average verse length in the OT vs NT are comparable,
with the OT having an average verse length of about 136 words vs the NT's average of 118 words in a verse.
Moving to question 2 we see a very significant difference in the use of the word 'lord' in the NT vs OT. 
The OT uses 'lord' 58,300 times and the NT only uses it 5,900 times. 'Lord' is seen over 52,000 more times
in the OT than in the NT. The graph demonstrates that in the NT verses are typically right around 100 to 120 words
in length. We can assume that the NT is shorter than the OT based off the answers to these three questions.