---
title: "Case9"
author: "Mallory Dickerson"
date: "11/2/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyquant)
library(dygraphs)
library(tidyverse)
library(timetk)
library(lubridate)
```



## stock function stuff
```{r}
start <- today() - years(5)
end <- today()

stock_calc <- function(tickers_today) {
  stocks <- tq_get(tickers_today, get = "stock.prices", from = start, to = end)
  combinedplot <- stocks %>%
  select(symbol, date, adjusted) %>%
  pivot_wider(names_from = symbol, values_from = adjusted) %>%
  tk_xts(date_var = date)
dygraph(combinedplot)
}

##this is what will change, just put in new stocks
tickers <- c("CXW", "F", "GM", "KR", "WDC", "NKE","T", "WDAY", "WFC", "WMT")


stock_calc(tickers)
```


## volume chart
```{r}
volume <- function(tickers_today) {
  tq_get(tickers_today, get = "stock.prices", from = start, to = end) %>%
    ggplot(aes(x = date, y = volume/100000, color = symbol)) +
    geom_line() +
    labs(
      x = "Date",
      y = "Volume Divided by 100,000",
      title = "Stock Volume Chart"
    ) +
    theme_tq()
}

volume(tickers)

```

I chose the first graph visualization simply because I used it in the task as well and found it very effective
in showing the best or best performing stock over time. It clearly demonstrates that WDAY WMT and NKE have the 
most expensive shares of stock.

The second graph I chose a line graph because we are looking at stock volume over time. I wanted a more readable
scale so I chose to divide it by 100000 and just label the axis so that is clear. 