---
title: "Case12"
author: "Mallory Dickerson"
date: "11/17/2022"
output: 
  html_document:
    keep_md: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(downloader)
library(gganimate)
library(ggplot2)
```
## reading in data
```{r}
avocado <- read_csv("avocado.csv", col_names = c("count", "date", "avgprice", "totalvol", "4046", "4225", "4770", "totalbags", "smallbags", "largebags", "xlargebags", "type", "year", "region"), skip = 1)
```

## seperating data into the specific cities given
```{r}
avocado_cities <- avocado %>%
  filter(! region %in% c("California", "GreatLakes", "MidSouth", "Northeast", "NorthernNewEngland", "Plains", "SouthCentral", "Southeast", "TotalUS", "West", "WestTexNewMexico"))
head(avocado_cities)
```

## seperating it into CA
```{r}
avocado_state <- avocado %>%
  filter(region == "California")
```

## seperaring into regions
```{r}
avocado_regions <- avocado %>%
  filter(region %in% c("GreatLakes", "MidSouth", "Northeast","NorthernNewEngland", "Plains", "SouthCentral", "Southeast","West", "WestTexNewMexico"))
head(avocado_regions)
```

## total us 
```{r}
avocado_totalUS <- avocado %>%
  filter(region == "TotalUS")
```

## creating visualizations
```{r}
avocadoplot <- ggplot(avocado_totalUS) +
  geom_point(aes(x = largebags/1000, y = avgprice)) +
  theme_bw() +
  # gganimate specific bits:
  labs(title = 'Year: {frame_time}', x = 'number of largebags sold divided by 1000', y = 'Average Price') +
  transition_time(year) +
  ease_aes('sine-in-out')

avocadoplot


avocadoplot <- ggplot(avocado_totalUS) +
  geom_point(aes(x = smallbags/1000, y = avgprice)) +
  theme_bw() +
  # gganimate specific bits:
  labs(title = 'Year: {frame_time}', x = 'number of smallbags sold divided by 1000', y = 'Average Price') +
  transition_time(year) +
  ease_aes('sine-in-out')


```

```{r}
region_plot <- ggplot(avocado_regions, aes(x = totalvol, y = avgprice, color = region)) +
  geom_line() +
  scale_color_viridis_d() +
  facet_wrap(~region) +
  labs(x = "Total Volume", y = "Average Price", title = "Avocado Price by Volume") +
  theme(legend.position = "top") +
  theme_bw()
region_plot + transition_reveal(date)
```

```{r}
cities_plot <- ggplot(avocado_cities, aes(x = totalvol, y = avgprice, color = region)) +
  geom_line() +
  scale_color_viridis_d() +
  labs(x = "Total Volume", y = "Average Price", title = "Avocado Price by Volume") +
  theme(legend.position = "top") +
  theme_bw()
cities_plot + transition_reveal(date)
```

##analyzing stock
```{r}
library(tidyquant)
library(dygraphs)
library(tidyverse)
library(timetk)
```

```{r}
start <- today() - years(1)
end <- today()
CVGW_prices <- tq_get("CVGW", get = "stock.prices", from = start, to = end)
CVGW_prices
CVGW_monthly <- CVGW_prices %>%
  tq_transmute(adjusted, mutate_fun = monthlyReturn)

avo_prices <- tq_get("AVO", get = "stock.prices", from = start, to = end)
avo_prices
avo_monthly <- avo_prices %>%
  tq_transmute(adjusted, mutate_fun = monthlyReturn)
avo_monthly

combined <- tq_get(c("CVGW", "AVO"), get = "stock.prices", from = start, to = end)


combinedplot <- combined %>%
  group_by(symbol) %>%
  plot_time_series(date, adjusted, 
                   .facet_ncol = 3,
                   .interactive = FALSE)
combinedplot
```
It does not look like a very good investment going forward. However, it does look like AVO is rebounding but not 
on a trend line with a significant amount of growth potential in the near future. CVGW has higher monthly returns,
but it has been falling off dramatically in recent months.

