---
title: "Task17"
author: "Mallory Dickerson"
date: "10/27/2022"
output: 
  html_document:
    keep_md: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(lubridate)
library(tidyquant)
```

## picking stocks

```{r}
## my stocks
stock1 <- "TGT"

stock2 <- "ANF"

stock3 <- "AEO"

## my friends stocks
stock4 <- "NKE"

stock5 <- "LULU"

stock6 <- "UA"

```


## pulling price performance for my stocks
TARGET
```{r}
start <- today() - years(1)
end <- today()
target_prices <- tq_get(stock1, get = "stock.prices", from = start, to = end)
target_prices

target_monthly <- target_prices %>%
  tq_transmute(adjusted, mutate_fun = monthlyReturn)


```

ABERCROMBIE AND FITCH
```{r}
anf_prices <- tq_get(stock2, get = "stock.prices", from = start, to = end)
anf_prices

anf_monthly <- anf_prices %>%
  tq_transmute(adjusted, mutate_fun = monthlyReturn)
anf_monthly
```
AMERICAN EAGLE
```{r}
aeo_prices <- tq_get(stock3, get = "stock.prices", from = start, to = end)
aeo_prices

aeo_monthly <- aeo_prices %>%
  tq_transmute(adjusted, mutate_fun = monthlyReturn)
aeo_monthly
```
## price performance for friend
NIKE
```{r}
nike_prices <- tq_get(stock4, get = "stock.prices", from = start, to = end)
nike_prices

nike_monthly <- nike_prices %>%
  tq_transmute(adjusted, mutate_fun = monthlyReturn)
nike_monthly
```
LULULEMON
```{r}
lulu_prices <- tq_get(stock5, get = "stock.prices", from = start, to = end)
lulu_prices

lulu_monthly <- lulu_prices %>%
  tq_transmute(adjusted, mutate_fun = monthlyReturn)
lulu_monthly
```
UNDER ARMOUR
```{r}
ua_prices <- tq_get(stock6, get = "stock.prices", from = start, to = end)
ua_prices

ua_monthly <- ua_prices %>%
  tq_transmute(adjusted, mutate_fun = monthlyReturn)
ua_monthly
```
## viz
```{r}
library(timetk)
my_stocks <- tq_get(c(stock1, stock2, stock3), get = "stock.prices", from = start, to = end)
my_stocks

friend_stocks <- tq_get(c(stock4, stock5, stock6), get = "stock.prices", from = start, to = end)
friend_stocks

combined <- tq_get(c(stock1,stock2,stock3,stock4,stock5,stock6), get = "stock.prices", from = start, to = end)


combined %>%
  group_by(symbol) %>%
  plot_time_series(date, adjusted, 
                   .facet_ncol = 6,
                   .interactive = FALSE)

my_stocks %>%
  group_by(symbol) %>%
  plot_time_series(date, adjusted, 
                   .facet_ncol = 3,
                   .interactive = FALSE)

friend_stocks %>%
  group_by(symbol) %>%
  plot_time_series(date, adjusted, 
                   .facet_ncol = 3,
                   .interactive = FALSE)

library(DT)
library(dygraphs)
library(timetk)

combinedplot <- combined %>%
  select(symbol, date, adjusted) %>%
  pivot_wider(names_from = symbol, values_from = adjusted) %>%
  tk_xts(date_var = date)
dygraph(combinedplot)
```

```{r}
library(timetk)

combined %>%
  filter(symbol == "LULU") %>%
  plot_time_series(date, adjusted, 
                   .interactive = FALSE,
                   .x_lab = "Date",
                   .y_lab = "Adjusted Value of Stock Price",
                   .title = "Lululemon Stock Price Between October 2021 to October 2022")
  

```
```{r}
combined %>%
  filter(symbol == "TGT") %>%
  plot_time_series(date, adjusted,
                   .interactive = FALSE,
                   .x_lab = "Date",
                   .y_lab = "Adjusted Value of Stock Price",
                   .title = "Target Stock Price Between October 2021 to October 2022")
```

I chose to first display all the chosen stocks in order to easily see the best performing one and 
in the process of doing so I realized that Target and Lululemon had similar fluctuations in stock prices which can
perhaps be attributed to similar forces acting in the retail market. I chose to display the top two stocks, 1 from
my chosen stocks and 1 from my friends chosen stocks. I wanted to compare with a trend line to show more clearly 
the starting share value of the stock to the ending share value of the stock.
