---
title: "Case10"
author: "Mallory Dickerson"
date: "11/6/2022"
output: 
  html_document:
    keep_md: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(USAboundaries)
library(downloader)
library(maps)
```

```{r}
permits <- tempfile()
download.file("https://github.com/WJC-Data-Science/DTS350/raw/master/permits.csv", "permits")
permits <- read_csv("permits")
head(permits)
```
```{r}
s_codes <- state_codes %>%
  mutate(state = as.integer(state_code))
head(s_codes)
```

```{r}
permits_data <- left_join(permits, s_codes, by = "state") %>%
  group_by(state_name, year) %>%
  summarize(across(value, sum))

head(permits_data)
```
## permits per state graph
```{r}
permits_by_state <- ggplot(data = permits_data, aes(x = year, y = value/1000, color = state_name)) +
  geom_point() +
  geom_line() +
  geom_vline(xintercept = 2008, linetype = "dotted") +
  labs(x = "Year",
       y = "Value Divided by 1000",
       title = "Permits per Year by State") +
  theme_bw()
    
permits_by_state  
```

```{r}
top_states_recession_permits <- permits_data %>%
  filter(year == 2006 | year == 2007 | year == 2008 | year == 2009) %>%
  filter(value >= 150000)

head(top_states_recession_permits)

ggplot(data = top_states_recession_permits, aes(x = year, y = value/1000, color = state_name)) +
  geom_point() +
  geom_line() +
  labs(x = "Year",
       y = "Housing Permit Count Divided by 1000",
       title = "Top 5 Housing Permit States Leading up to the Recession") +
  theme_bw()
  
```
Looking at the top housing permits states a few years before the crash and a year after.

## sort of state geo plot
```{r}
library(geofacet)
recession_permits <- permits_data %>%
  filter(year == 2006 | year == 2007 | year == 2008)

library(ggplot2)

ggplot(recession_permits, aes(year, value/10000, fill = value)) +
  geom_col() +
  coord_flip() +
  facet_geo(~ state_name) +
  xlab("Housing Permit Count Divided by ten thousand") +
  ylab("Year") +
  theme_bw()
```

```{r}
Missouri <- permits_data %>%
  filter(state_name == 'Missouri') %>%
  ggplot(aes(x = year, y = value)) +
  geom_point() +
  geom_line() +
  labs(x = 'Year', 
       y = 'Permit Amount',
       title = "Missouri Housing Permits") +
  theme_bw()

Missouri
```

I chose line graphs mostly because we are looking at permit amounts over time. The closest I could get to a
map using the data was the geofacet. I chose to do geom_col on that just because it was extremely hard to read
as a line graph and you can still see the decrease in permits, especially in states like california, texas,
georgia, the carolinas, and florida. 