---
title: "Case10"
author: "Mallory Dickerson"
date: "11/6/2022"
output: 
  html_document:
    keep_md: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(USAboundaries)
library(downloader)
library(maps)
library(ggplot2)

```

```{r}
permits <- tempfile()
download.file("https://github.com/WJC-Data-Science/DTS350/raw/master/permits.csv", "permits")
permits <- read_csv("permits")
head(permits)
```

## FIPS setup stuff
```{r}

counties <- us_counties()

FIPS <- permits %>%
  mutate(state = as.character(state), stateFIPS = str_pad(state, 2,pad = "0")) %>%
  mutate(county = as.character(county), countyFIPS = str_pad(county, 3,pad = "0"))
FIPS


FIPS$geoid <- paste0(FIPS$stateFIPS, FIPS$countyFIPS)
head(FIPS)

counties <- counties[, !duplicated(colnames(counties))]
head(counties)

fips_data <- merge(counties, FIPS, by = "geoid")
head(fips_data)
```


## permits per state graph
```{r}
totals <- fips_data %>%
  filter(variable == "Single Family") %>%
  group_by(state_name, StateAbbr, year) %>%
  summarize(across(value,sum))

tail(totals)



permits_by_state <- ggplot(data = totals, aes(x = year, y = value, color = StateAbbr)) +
  geom_point() +
  geom_line(data = totals, aes(x = year, y = value)) +
  geom_vline(xintercept = 2008, linetype = "dotted") +
  labs(x = "Year",
       y = "Single Family Permit Amounts",
       title = "Permits per Year by State") +
  theme_bw()
    
permits_by_state  
```

```{r}
top_states_recession_permits <- totals %>%
  filter(year == 2005 | year == 2006 | year == 2007 | year == 2008 | year == 2009 | year == 2010) %>%
  filter(StateAbbr == "AZ" | StateAbbr == "CA" | StateAbbr == "FL" | StateAbbr == "GA" | StateAbbr == "TX" | StateAbbr == "NC")

head(top_states_recession_permits)

top6 <- ggplot(data = top_states_recession_permits, aes(x = year, y = value, color = state_name)) +
  geom_point() +
  geom_line() +
  labs(x = "Year",
       y = "Single Family Housing Permit Count",
       title = "Top 6 Single Family Housing Permit States Leading up to the Recession") +
  theme_bw()
top6 
```
Looking at the top housing permits states a few years before the crash and a year after.

## sort of state geo plot
```{r}
library(geofacet)
recession_permits <- totals %>%
  filter(year == 2006 | year == 2007 | year == 2008)

library(ggplot2)

ggplot(recession_permits, aes(year, value/10000, fill = value)) +
  geom_col() +
  coord_flip() +
  facet_geo(~ StateAbbr) +
  xlab("Single Family Housing Permit Count Divided by ten thousand") +
  ylab("Year") +
  theme_bw()
```

##East Coast Housing Themes
```{r}
east_coast <- totals %>%
  filter(year >= 1990) %>%
  filter(StateAbbr == "NY" | StateAbbr == "CT" | StateAbbr == "NJ" | StateAbbr == "MA" | StateAbbr == "NH" | StateAbbr == "VT")


east <- ggplot(data = east_coast, aes(x = year, y = value, color = state_name)) +
  geom_point() +
  geom_line() +
  labs(x = "Year",
       y = "Single Family Housing Permit Count",
       title = "Single Family Housing Permit States ") +
  theme_bw()
east
```


```{r}
Missouri <- totals %>%
  filter(state_name == 'Missouri') %>%
  ggplot(aes(x = year, y = value)) +
  geom_point() +
  geom_line() +
  labs(x = 'Year', 
       y = 'Permit Amount',
       title = "Missouri Housing Permits") +
  theme_bw()

Missouri
```
I chose line graphs mostly because we are looking at permit amounts over time. The closest I could get to a
map using the data was the geofacet. I chose to do geom_col on that just because it was extremely hard to read
as a line graph. 