---
title: "Task5"
author: "Mallory Dickerson"
date: "9/8/2022"
output: 
  html_document:
    keep_md: true
    code_folding: 'hide'
---

```{r}
library(tidyverse)
library(downloader)
library(knitr)
```

```{r reading in data}
SoloData <- read_csv("solo-artist-followers.csv")
BillboardData <- read_csv("billboard-hits.csv")
```


```{r commenting on the data}
str(SoloData)
str(BillboardData)
```
SoloData is a tibble of 139 rows and 5 columns. Each column variable is a character. BillboardData is a tibble of 456 rows and 5 columns. 'name', 'band', and 'title' are characters and peak_date is a Date datatype. 'peak_rank' is numeric. I believe it imported correctly.

```{r removing singers who dont have at least 6 top 100 hits}
head(BillboardData)
head(SoloData)

times_top_100 <- BillboardData %>%
  filter(is.na(band) == FALSE) %>%
  group_by(name, band) %>%
  summarize(appearance = n()) %>%
  filter(appearance >= 6, na.rm = TRUE)

times_top_100

colorline <- BillboardData %>%
  filter(is.na(band) == FALSE) %>%
  filter(name %in% times_top_100$name)

colorline

blackline <- BillboardData %>%
  filter(is.na(band) == TRUE) %>%
  filter(name %in% times_top_100$band) %>%
  mutate(band = name)

blackline


```


```{r}
graphpop_bands <- ggplot() +
  geom_point(colorline, mapping = aes(x = peak_date, y = peak_rank, color = name)) +
  geom_line(colorline, mapping = aes(x = peak_date, y = peak_rank, color = name)) +
  geom_point(blackline, mapping = aes(x = peak_date, y = peak_rank), color = "black") +
  geom_line(blackline,  mapping = aes(x = peak_date, y = peak_rank), color = "black", linetype = "dotted") +
  facet_wrap(~ band, scales = "free")


graphpop_bands

```
Beyonce has consistently the most top 100 hits of any solo artists. However, Adventura appears to be a band who was most consistently in the top 100.





Options for Data for Project:

1. 
https://github.com/fivethirtyeight/data/tree/master/study-drugs
some info:
Some of the datasets are confidential. The data includes information regarding using a variety of drugs as well as alcohol. It identifies first use as well as ongoing usage. 

drugdata <- read_csv ("DS1 National Survey on Drug Use and Health, 2013.csv")

the variables in this dataset are all numeric

2.
https://daac.ornl.gov/cgi-bin/dsviewer.pl?ds_id=1934
some info:
This data identifies over 70 variables related to CO2 exchange in the atmosphere. The data is related to the arctic with 244 observation sites related specifically to the tundra.

arctic <- read_csv("Arctic_Boreal_CO2_Flux.csv")

data types are either some sort of numeric data, or date, or character.

3.
https://academictorrents.com/details/e24e083cc337695bb84a2b68707695579c0ab4d8
some info:
Looks at a set of factors that measure and influence student learning. The data looks at 115 first year Engineering majors attending a university in Italy. (University of Genoa)

Finalgrades <- read_csv(final_grades.xlsx)
grades <- read_csv(intermediate_grades.xlsx)
data types are either dates, characters, or numbers
